A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
turker map
Making changes to the intro

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skill claims by measuring their ability to correctly translate words, and by geolocating workers to see if they reside in countries where the languages are likely to be spoken. Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 100 languages.  Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen it.  Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.  We use this data to recommend languages with the largest speaker populations as good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.

@@

\section{Overview}
Crowdsourcing has become a key mechanism for collecting data for natural language processing research. Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds promise for enabling future language technologies. Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data. As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.

We evaluate the language skills of bilingual workers on Amazon's Mechanical Turk, and their ability to provide translated data for statistical machine translation. Collecting parallel translated texts has traditionally been assumed to require a higher level of expertise than what is available from non-professional crowd workers. However, with an increasing number of active crowd workers located outside of the United States, the potential to access fluent speakers of lower resource languages makes crowdsourcing an attractive resource for translation.

@@

>>>>

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skill claims by measuring their ability to correctly translate words, and by geolocating workers to see if they reside in countries where the languages are likely to be spoken. Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 119 languages.  Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would complete it.  Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.  We use this data to recommend languages with the largest speaker populations as good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.

@@

\section{Introduction}
Crowdsourcing is a promising new mechanism for collecting data for natural language processing research. Access to a fast, cheap, and flexible workforce allows us to collect new types of data, potentially enabling new language technologies.
% ccb - todo - combine these sentences:
Because crowdsourcing platforms like Amazon Mechanical Turk (MTurk) give researchers access to a worldwide workforce, one obvious application of crowdsourcing is the creation of multilingual technologies. 
With an increasing number of active crowd workers located outside of the United States, there is even the potential to reach fluent speakers of lower resource languages.
In this paper, we present the first large-scale demographic study of the languages spoken by workers on MTurk.

%Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds promise for enabling future language technologies. Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data. As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.
%We evaluate the language skills of bilingual workers on Amazon's Mechanical Turk, and their ability to provide translated data for statistical machine translation. Collecting parallel translated texts has traditionally been assumed to require a higher level of expertise than what is available from non-professional crowd workers. However, with an increasing number of active crowd workers located outside of the United States, the potential to access fluent speakers of lower resource languages makes crowdsourcing an attractive resource for translation.

@@

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/turkermap}
\caption{}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
